%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Luka Mihailović} \\ \vspace{1pt}
    \small +381-63-7077-330 $|$ \href{mailto:luka@lukam.xyz}{\underline{luka@lukam.xyz}} $|$ 
    \href{https://www.linkedin.com/in/luka-mihailović/}{\underline{linkedin.com/in/luka-mihailović}} $|$
    \href{https://lukam.xyz}{\underline{lukam.xyz}} $|$
    \href{https://github.com/lmihailovic}{\underline{github.com/lmihailovic}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Faculty of Computing}{Belgrade, Serbia}
      {Master of Computer Applications --- MCA, Information Technology}{Oct. 2025 -- 2027}
    \resumeSubheading
      {Faculty of Computing}{Belgrade, Serbia}
      {Bachelor of Applied Science --- BASc, Information Technology}{Oct. 2022 -- Sep. 2025}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Development Intern}{July 2025}
      {MNO Company}{Belgrade, Serbia}
      \resumeItemListStart
        \resumeItem{Developed an advanced theme for company's website with the Hugo static site generator using Go's text/template and text/html libraries.}
        \resumeItem{Researched Go and developed thorough understanding of it, writing docs for the team to further maintain my internship's project.}
        \resumeItem{Implemented an advanced responsive frontend design using vanilla CSS with semantic HTML.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Head of Information Technology Department}{Feb. 2023 -- Present}
      {Argo Student Robotics Team}{Belgrade, Serbia}
      \resumeItemListStart
        \resumeItem{Communicate with the board of directors about the team's IT needs.}
        \resumeItem{Coordinating with two teams under my leadership to simultaneously perform several software development tasks.}
        \resumeItem{Personally took care of IT administration, managing user accounts, groups, permissions and making sure our server runs without downtime.}
    \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/lmihailovic/sugo}{sugo}} $|$ \emph{Go, Git}}{Aug. 2025 -- Sep. 2025}
          \resumeItemListStart
            \resumeItem{Developed a simple and flexible static-site generator using Go's standard library.}
            \resumeItem{Implemented dynamic menu abilities and site structure mimicking the user's content directory.}
            \resumeItem{Added an ability for a local live preview of the generated site.}
          \resumeItemListEnd
    \resumeProjectHeading
        {\textbf{\href{https://github.com/lmihailovic/toctou-demo}{toctou-demo}} $|$ \emph{Go, PostgreSQL, Docker, Git}}{June 2026}
        \resumeItemListStart
          \resumeItem{Collaborated on a group project demonstrating and mitigating TOCTOU race condition vulnerabilities in a web application.}
          \resumeItem{Implemented the secure version of the application using \texttt{sync.Mutex} and database transactions to prevent double-spend attacks.}
          \resumeItem{Wrote comprehensive documentation about how the attack works and how to protect against it.}
        \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://github.com/lmihailovic/Strong-eCourses}{Strong eCourses}} $|$ \emph{C\#, ASP.NET, MongoDB, Taiga, Git}}{April 2025 -- May 2025}
          \resumeItemListStart
            \resumeItem{Developed a web application platform for managing online courses as a group project.}
            \resumeItem{Served as team leader, managing agile workflows with Taiga and resolving merge conflicts on the project's Git repository.}
            \resumeItem{Implemented user authentication with ASP.NET Identity.}
            \resumeItem{Utilised MongoDB for project database, allowing high throughput of requested data.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C\#, Go, C/C++, Python, PHP, SQL, HTML/CSS, \LaTeX} \\
     \textbf{Frameworks}{: ASP.NET, Laravel, Flask} \\
     \textbf{Developer Tools}{: Git, Docker, Google Cloud Platform, VS Code, Visual Studio, Rider, GoLand, PhpStorm, PyCharm} \\
     \textbf{Systems}{: Arch/Rocky Linux, systemd, SSH, user/group management, server administration} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}

